---
title: "Exercise 2: Pick your own adventure"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
---

<style>
.aim {
  padding-left: 40px;
}

.aim:before {
  position: absolute;
  content: "🎯";
  margin-left: -20px;
}


.target {
  border: 3px solid black;
  padding: 10px;
  padding-top: 35px;
  margin-bottom: 10px;
}
.target:before {
  position: absolute;
  content: "🎯 your target plot";
  padding: 5px;
  margin-left: -13px;
  margin-top: -38px;
  background-color: #003366;
  font-size: 12pt;
  border: 3px solid black;
  color: white;
}
.solution {
  padding-top: 20px;
}
.solution:before {
  position: absolute;
  content: "solution";
  text-decoration: underline;
  font-size: 12pt;
  font-weight: bold;
  margin-top: -20px;
  color: rgba(0, 51, 102, 0.3);
}
</style>
```{r, include = FALSE}
library(learnr)
knitr::knit_hooks$set(class = function(before, options, envir) {
  if(before) {
    sprintf("<div class='%s'>", options$class)
  } else {
    "</div>"
  }
})
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE
)
```


## Objective  {data-progressive=FALSE}

::: aim

In this exercise, there are several data that may be of interest to you. Pick your own adventure by selecting the data of your interest, study the variables that contain it and try visualising aspects of the data. There are no correct answers here. There are some code provided to aid you in how to begin.

:::


```{r pkgs, message = FALSE, warning = FALSE}
library(tidyverse) # contains ggplot2
library(edvr.workshop) # contains local Aussie datasets
```

## APRA: hospital treatment coverage data

```{r data-apra}
str(apra_hospital_coverage)
```

```{r apra, exercise = TRUE}
ggplot(apra_hospital_coverage, aes(Quarter, AUST)) +
  geom_line()
```

## Australian Census: Birth place by sex

```{r data-census}
str(census_bpsex)
```

```{r census, exercise = TRUE}
census_bpsex %>% 
  filter(birth != "Total") %>% 
  mutate(birth = fct_reorder(birth, percentage)) %>% 
  ggplot(aes(percentage, birth)) +
  geom_col()
```

## City of Casey: Summary residential community emissions

```{r data-casey}
str(casey_emissions)
```

```{r casey, exercise = TRUE}

```

## Covid-19 data for Australia

```{r data-covid}
str(au_covid)
```

```{r covid, exercise = TRUE}
casey_emissions %>% 
  filter(!is.na(total_elect)) %>% 
  ggplot() +
  geom_sf(aes(geometry = geometry, fill = total_elect))
```


## EPA Vic: Air Watch Data

```{r data-epa}
str(epa_airquality)
```

```{r epa, exercise = TRUE}
epa_airquality %>% 
  filter(param_id == "NO") %>% 
  ggplot(aes(sample_datetime, value)) + 
  geom_line() +
  facet_grid(sp_name ~ .)
```


