---
title: "Exercise 1: Getting started with ggplot2"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
---

<style>
.aim {
  padding-left: 40px;
}

.aim:before {
  position: absolute;
  content: "🎯";
  margin-left: -20px;
}


.target {
  border: 3px solid black;
  padding: 10px;
  padding-top: 35px;
  margin-bottom: 10px;
}
.target:before {
  position: absolute;
  content: "🎯 your target plot";
  padding: 5px;
  margin-left: -13px;
  margin-top: -38px;
  background-color: #003366;
  font-size: 12pt;
  border: 3px solid black;
  color: white;
}
.solution {
  padding-top: 20px;
}
.solution:before {
  position: absolute;
  content: "solution";
  text-decoration: underline;
  font-size: 12pt;
  font-weight: bold;
  margin-top: -20px;
  color: rgba(0, 51, 102, 0.3);
}
</style>
```{r, include = FALSE}
library(learnr)
library(maps)
knitr::knit_hooks$set(class = function(before, options, envir) {
  if(before) {
    sprintf("<div class='%s'>", options$class)
  } else {
    "</div>"
  }
})
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE
)
```


## Objective  {data-progressive=FALSE}

::: aim

* For each exercise, you will be shown the structure of the dataset and then make a targetted plot shown. 

* You can find more details about the dataset by looking at the documentation in your R console, e.g. enter `?ggplot2::diamonds` for information of the diamonds dataset.

* Choose the level most appropriate to you from the menu on the left:
   * _Easy_ for beginners 
   * _Hard_ for those experienced

:::

## Easy

```{r pkgs, message = FALSE, warning = FALSE}
library(tidyverse) # contains ggplot2
library(agridat) # for datasets
```


### Exercise 1


```{r pig-data}
str(crampton.pig)
```

```{r ex01s, echo = FALSE, class = "target"}
ggplot(crampton.pig, aes(feed)) + 
  geom_density() 
```

```{r ex01, exercise = TRUE}
ggplot(crampton.pig, aes(___)) + 
  geom_density() 
```

```{r ex01-solution, ref.label="ex01s"}
```

### Exercise 2

Now try changing the y-axis so it shows `count` instead of `density`.

```{r ex02s, echo = FALSE, class = "target"}
ggplot(crampton.pig, aes(feed)) + 
  geom_density(aes(y = after_stat(count))) 
```

```{r ex02, exercise = TRUE}
ggplot(crampton.pig, aes(___)) + 
  geom____(aes(y = ___)) 
```

```{r ex02-solution, ref.label="ex02s"}
```

### Exercise 3

```{r ex03s, echo = FALSE, class = "target"}
ggplot(crampton.pig, aes(feed)) + 
  geom_boxplot() 
```

```{r ex03, exercise = TRUE}
ggplot(crampton.pig, aes(___)) + 
  geom____() 
```

```{r ex03-solution, ref.label="ex03s"}
```


### Exercise 4

```{r ex04s, echo = FALSE, class = "target"}
ggplot(crampton.pig, aes(weight1, weight2, color = treatment, size = feed)) + 
  geom_point()
```

```{r ex04, exercise = TRUE}
ggplot(crampton.pig, aes(___, ___, color = ___, size = ___)) + 
  geom____()
```

```{r ex04-solution, ref.label="ex04s"}
```

### Exercise 5

```{r ex05s, echo = FALSE, class = "target"}
ggplot(crampton.pig, aes(rep, treatment, fill = weight2 - weight1)) + 
  geom_tile(color = "black", linewidth = 2)
```

```{r ex05, exercise = TRUE}
ggplot(crampton.pig, aes(___, ___, fill = ___)) + 
  geom_tile(color = "black", linewidth = 2)
```

```{r ex05-solution, ref.label="ex05s"}
```

### Exercise 6

```{r ex06s, echo = FALSE, class = "target"}
ggplot(crampton.pig, aes(weight2 - weight1, fill = treatment)) + 
  geom_density(alpha = 0.7) 
```

```{r ex06, exercise = TRUE}
ggplot(crampton.pig, aes(___, fill = ___)) + 
  geom_density(alpha = 0.7) 
```

```{r ex06-solution, ref.label="ex06s"}
```



### Exercise 7

```{r}
str(diamonds)
```


```{r ex07s, echo = FALSE, class = "target", message = FALSE}
ggplot(diamonds, aes(price)) + 
  geom_histogram() 
```

```{r ex07, exercise = TRUE}
ggplot(diamonds, aes(___)) + 
  geom____() 
```

```{r ex07-solution, ref.label="ex07s"}
```

### Exercise 8

Try changing the bin width to see how the histogram changes. 

```{r ex08s, echo = FALSE, class = "target", message = FALSE}
ggplot(diamonds, aes(price)) + 
  geom_histogram(binwidth = 1) 
```

```{r ex08, exercise = TRUE}
ggplot(diamonds, aes(___)) + 
  geom____(___ = 1) 
```

```{r ex08-solution, ref.label="ex08s"}
```

### Exercise 9

```{r ex09s, echo = FALSE, class = "target", message = FALSE}
ggplot(diamonds, aes(price)) + 
  stat_bin(geom = "line")
```

```{r ex09, exercise = TRUE}
ggplot(diamonds, aes(___)) + 
  stat____(___ = "line") 
```

```{r ex09-solution, ref.label="ex09s"}
```



### Exercise 10

```{r ex10s, echo = FALSE, class = "target", message = FALSE}
ggplot(diamonds, aes(clarity, price, fill = cut)) + 
  geom_boxplot()
```

```{r ex10, exercise = TRUE}
ggplot(diamonds, aes(___, ___, fill = ___)) + 
  geom____()
```

```{r ex10-solution, ref.label="ex10s"}
```


### Exercise 11

```{r ex11s, echo = FALSE, class = "target", message = FALSE}
ggplot(diamonds, aes(carat, price)) + 
  geom_density_2d_filled()
```

```{r ex11, exercise = TRUE}
ggplot(heart2, aes(___, ___)) + 
  geom_density_2d_filled()
```

```{r ex11-solution, ref.label="ex11s"}
```


### Exercise 12

```{r ex12s, echo = FALSE, class = "target", message = FALSE}
ggplot(diamonds, aes(carat, price)) + 
  geom_hex()
```

```{r ex12, exercise = TRUE}
ggplot(diamonds, aes(___, ___)) + 
  geom____()
```

```{r ex12-solution, ref.label="ex12s"}
```



This is the last question for the easy level! Well done getting to here!


## Hard

```{r}
str(nass.wheat)
str(nass.corn)
str(nass.soybean)
```

### Exercise 1

```{r hex01s, echo = FALSE, class = "target", message = FALSE, warning = FALSE}
wheat_corn_data <- left_join(nass.wheat, 
                             nass.corn, 
                             suffix = c("_wheat", "_corn"),
                             by = c("year", "state"))

ggplot(wheat_corn_data, aes(yield_corn, yield_wheat)) + 
  geom_point(aes(color = year)) +
  geom_density_2d(color = "black") 
```

```{r hex01, exercise = TRUE}
wheat_corn_data <- ___

ggplot(wheat_corn_data, aes(___, ___)) + 
  geom____(aes(color = ___)) +
  geom_density_2d(color = "black") 
```

```{r hex01-hint}
wheat_corn_data <- left_join(nass.wheat, 
                             nass.corn, 
                             suffix = c("_wheat", "_corn"),
                             by = c("year", "state"))
```

```{r hex01-solution, ref.label="hex01s"}
```

### Exercise 2

```{r hex02s, echo = FALSE, class = "target"}
crops_data <- bind_rows(mutate(nass.wheat, crop = "Wheat"),
                        mutate(nass.corn, crop = "Corn"),
                        mutate(nass.soybean, crop = "Soy")) 

ggplot(crops_data, aes(crop, yield)) + 
  geom_violin() + 
  geom_boxplot(width = 0.1)
```

```{r hex02, exercise = TRUE}
crops_data <- ___

ggplot(crops_data, aes(___, ___)) + 
  geom____() + 
  geom____(width = 0.1)
```

```{r hex02-hint}
crops_data <- bind_rows(mutate(nass.wheat, crop = "Wheat"),
                        mutate(nass.corn, crop = "Corn"),
                        mutate(nass.soybean, crop = "Soy")) 
```

```{r hex02-solution, ref.label="hex02s"}
```


### Exercise 3

```{r hex03s, echo = FALSE, class = "target"}
wheat2011_data <- nass.wheat %>% 
  filter(year == 2011) 

highlight <- function(.data) subset(.data, acres > 4000000 | yield > 80)

ggplot(wheat2011_data, aes(acres, yield)) + 
  geom_point() + 
  geom_point(data = highlight, color = "red") + 
  geom_text(data = highlight, aes(label = state), nudge_y = 5) 
```

```{r hex03, exercise = TRUE}
wheat2011_data <- nass.wheat %>% 
  ___(year == 2011) 

highlight <- function(.data) subset(.data, acres > 4000000 | yield > 80)

ggplot(wheat2011_data, aes(___, yield)) + 
  ___() + 
  ___(data = ___, color = "red") + 
  geom_text(data = ___, aes(label = ___), nudge_y = 5) 
```

```{r hex03-solution, ref.label="hex03s"}
```

### Exercise 4

Let's draw a choropleth US map of the wheat yield in 2011. 

```{r hex04s, echo = FALSE, class = "target"}
wheat2011_data_with_map <- nass.wheat %>% 
  filter(year == 2011) %>% 
  mutate(region = tolower(state)) %>% 
  right_join(map_data("state"), by = "region")

ggplot(wheat2011_data_with_map, aes(long, lat)) + 
  geom_polygon(aes(group = group, fill = yield), color = "black") +
  annotate("label", x = -120, y = 27, label = "2011", size = 8)
```

```{r hex04-hint}
wheat2011_data_with_map <- nass.wheat %>% 
  filter(year == 2011) %>% 
  mutate(region = tolower(state)) %>% 
  right_join(map_data("state"), by = "region")
```


```{r hex04, exercise = TRUE}
wheat2011_data_with_map <- nass.wheat %>% 
  ___

ggplot(wheat2011_data_with_map, aes(___, ___)) + 
  geom_polygon(aes(___), color = "black") +
  ___(___, x = -120, y = 27, label = "2011", size = 8)
```

```{r hex04-solution, ref.label="hex04s"}
```


### Exercise 5

Consider fitting a model to the log of the yield of wheat (with base 10) with year as a covariate as shown below in the first line of code. Try constructing a residual plot based on this fit. What do you think of the fit of the model?

```{r hex05s, echo = FALSE, class = "target"}
fit <- lm(log10(yield) ~ year, data = nass.wheat)

ggplot(nass.wheat, aes(year, residuals(fit))) + 
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey")
```

```{r hex05, exercise = TRUE}
fit <- lm(log10(yield) ~ year, data = nass.wheat)

ggplot(nass.wheat, aes(year, residuals(fit))) + 
  ___ + 
  geom____(yintercept = 0, linetype = "dashed", color = "grey")
```

```{r hex05-solution, ref.label="hex05s"}
```




### Exercise 6

```{r}
str(minnesota.barley.weather)
```


```{r hex06s, echo = FALSE, class = "target", fig.width = 7.5, fig.height = 6}
ggplot(minnesota.barley.weather, aes(year, max)) + 
  geom_point() + 
  facet_grid(site ~ mo) +
  guides(x = guide_axis(angle = 90))
```

```{r hex06, exercise = TRUE}
ggplot(minnesota.barley.weather, aes(___, ___)) + 
  geom____() + 
  facet____(___ ~ ___) +
  guides(x = ___(angle = 90))
```

```{r hex06-solution, ref.label="hex06s"}
```

### Exercise 7

```{r}
str(economics_long)
```

```{r hex07s, echo = FALSE, class = "target"}
ggplot(economics_long, aes(date, value01)) +
  # rename the facet variable
  geom_line(data = function(.data) rename(.data, var = variable), 
            color = "gray",
            aes(group = var)) +
  geom_line() +
  facet_wrap(~variable, 
             # relabel facet labels
             labeller = labeller(
               variable = c("pce" = "consumption",
                            "pop" = "population",
                            "psavert" = "savings rate",
                            "uempmed" = "unemployment duration",
                            "unemploy" = "unemployment"))) +
  labs(y = "Standardised values", 
       x = "Year",
       title = "US economic time series") 
```

```{r hex07, exercise = TRUE}
ggplot(economics_long, aes(___, value01)) +
  geom____(data = ___, 
            color = "gray",
            ___) +
  geom____() +
  facet____(~variable, 
             # relabel facet labels
             labeller = labeller(
               variable = c("pce" = "consumption",
                            "pop" = "population",
                            "psavert" = "savings rate",
                            "uempmed" = "unemployment duration",
                            "unemploy" = "unemployment"))) + 
  labs(___ = "Standardised values", 
       ___ = "Year",
       ___ = "US economic time series (standardised values)")
```

```{r hex07-solution, ref.label="hex07s"}
```


### Exercise 8

```{r}
str(economics_long)
```


```{r hex08s, echo = FALSE, class = "target"}
ggplot(economics_long, aes(date, value)) + 
  geom_line() + 
  facet_wrap(~variable, scale = "free_y") + 
  scale_y_continuous(labels = scales::comma) +
  labs(x = "Date", 
       y = "",
       title = "US economic time series")
```

```{r hex08, exercise = TRUE}
ggplot(economics_long, aes(date, value)) + 
  geom_line() + 
  facet_wrap(~variable, scale = "free_y") + 
  scale_y_continuous(labels = scales::comma) +
  labs(x = "Date", 
       y = "",
       title = "US economic time series")
```

```{r hex08-solution, ref.label="hex08s"}
```
